\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
scipy

We optimize two models, one for Training Set A and one for Training Set B.
For optimization, we use \code{scipy} l-bfgs-b (HOGG CHECK), starting at
an uninformed starting point in the $\theta$ space.
The optimization is of the objective function given in (HOGG WHAT EQUATION) above,
and although this optimization is not convex, it appears to converge to the
same good solution quickly and reliably from multiple different starting points.

>>>>

We optimize two models, one for Training Set A and one for Training Set B.
For optimization, we use \code{scipy.optimize} \acronym{L-BFGS-B}, starting at
an uninformed starting point in the $\theta$ space.
The optimization is of the objective function given in \equationname~(\ref{eq:objective}) above,
and although this optimization is not convex, it appears to converge to the
same good solution quickly and reliably from multiple different starting points.
